### 2017-02-14 docs/reports/experiments_MH-DTM/report_mh-dtm.tex
Decribing the experiment results (beginning).

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{float}

@@

\par

>>>>

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}

@@

\par The first experiment is focused on discovering the choice of the variances. To be more specific, the alpha update is based on three different variances were used: the `initial' variance $\sigma_0^2I$ to induce $\alpha_t$ at $t=0$, the `basic' variance $\sigma^2I$ to induce $\alpha_t$ at $t>0$, and the `proposed' variance $\delta^2I$ to induce $\alpha'_t$ at $t=0$; also, note that $\alpha'_t$ at $t>0$ were induced using the `basic' variance.

\par The experiment involved $500$ autoregressive iterations and $\sigma^2$ were set to $0.1$. The idea was to tune the model with different values of $\sigma_0$ and $\delta^2$; the choice of different values is illustrated in Figures 3, 4, 5 below.

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\textwidth]{var-init-10_var-prop-5_iter-500}
  \caption{The values of $\beta$ used in the generative process.}
  \label{fig:a}
\end{figure}
\begin{figure}[H]
        \begin{subfigure}[b]{0.33\textwidth}
                \includegraphics[width=\linewidth]{var-init-10_var-prop-5_iter-500}
                \caption{A gull}
                \label{fig:gull}
        \end{subfigure}%
        \begin{subfigure}[b]{0.33\textwidth}
                \includegraphics[width=\linewidth]{var-init-10_var-prop-5_iter-500}
                \caption{A gull2}
                \label{fig:gull2}
        \end{subfigure}%
        \begin{subfigure}[b]{0.33\textwidth}
                \includegraphics[width=\linewidth]{var-init-10_var-prop-5_iter-500}
                \caption{A tiger}
                \label{fig:tiger}
        \end{subfigure}
        \caption{Pictures of animals}\label{fig:animals}
\end{figure}
